### 2018-03-23 Writing/draft.tex
Slight title update
Chg first line abstract

\noindent{\Large \bf Influence of different modes of morphological character correlation on tree inference}
\bigskip

@@

\newpage
\begin{abstract}
Morphological characters for building phylogenies are assumed to be independent.
However, this assumption is nearly always wrong simply because of the nature of morphological integration of organisms.
Correlation between characters can originate from intra-organismal features, shared phylogenetic history or errors when coding or defining morphological characters.
Although the two first sources can be investigated by biologists \textit{a posteriori} and the third one can be avoided \textit{a priori} with good practices, phylogenetic software do not distinguish between any of them.

>>>>

\noindent{\Large \bf Influence of different modes of morphological character correlation on phylogenetic tree inference}
\bigskip

@@

\newpage
\begin{abstract}
Phylogenetic analysis algorithms require the assumption of character independence---a condition generally acknowledged to be violated by morphological data.
However, this assumption is nearly always wrong simply because of the nature of morphological integration of organisms.
Correlation between characters can originate from intra-organismal features, shared phylogenetic history or errors when coding or defining morphological characters.
Although the two first sources can be investigated by biologists \textit{a posteriori} and the third one can be avoided \textit{a priori} with good practices, phylogenetic software do not distinguish between any of them.
